\section{Model}

A firm's production process consists of a fixed sequence of steps $\mathcal{S}=(s_1,\ldots,s_m)$.
The firm can partition contiguous subsequences of steps into a sequence of tasks $\T=(T_1,\ldots,T_n)$ where $T_b=(s_i,\ldots,s_{i+\ell})$ for some $i$ and $\ell$.
The firm can also partition contiguous subsequences of the resulting tasks into jobs $\mathcal{J}=(J_1,\ldots,J_p)$.
Figure \ref{fig:hierarchical_production} provides an illustration for a production process with $m=7$ steps, $n=5$ tasks, and $p=3$ jobs.
The cost of any such partitioning depends on the time and skill needed for the component steps, the mode in which the step is completed, and the grouping of steps and tasks.
We discuss these in turn.
% \begin{figure}[ht!]
%   \begin{center}
%   \caption{Illustrative Example of a Firm's Production}
%   \label{fig:hierarchical_production}
  
%   \vspace{0.4cm}
%   \input{plots/hierarchical_production_illustration.tex}
%   \end{center}
  
%   \vspace{0.4cm}
%   \raggedright \footnotesize{\emph{Notes:} 
%   This figure illustrates how a firm aggregates steps into tasks and tasks into jobs. 
%   The top layer shows $m=7$ steps executed in manual (gray), automated (green), or augmented (orange) modes, with dashed boxes indicating task groupings. 
%   The middle layer aggregates steps into $n=5$ tasks, classified as human-executed tasks (olive) or AI chains (purple), with cyan dashed boxes indicating job groupings. 
%   The bottom layer aggregates tasks into $p=3$ jobs (cyan), each assigned to a separate worker. 
%   Vertical colored arrows show aggregation across layers, and horizontal arrows show production flow within each layer. 
%   Red curly arrows mark hand-off costs incurred at job boundaries, and can be traced from the bottom layer to the corresponding tasks and steps above. 
%   }
% \end{figure}




\subsection{Steps}
\label{sec:model.steps}

Each step can be completed either with AI assistance or manually (without AI).  
If the firm assigns step $i$ to manual execution (denoted by $\manualLetter$), it hires a human worker of skill level $\manualSkill{i}$ and pays for the time $\manualTime{i}$ required to complete the step without AI.  
Alternatively, if the firm assigns step $i$ to AI-assisted execution (denoted by $\AIletter$), it hires a human worker of (potentially different) skill level $\AIskill{i}$ and pays for the time $\AItime{i}$ spent completing the step in collaboration with AI.\footnote{
This could, for example, represent the time spent prompting an AI system and checking the response, or ``managing'' the AI.
}
Such a collaboration succeeds independently with some (step-dependent) probability $q_i=\alpha^{d_i}$ where $\alpha$ is the quality of the general purpose AI technology and $d_i$ represents how ``difficult'' step $i$ is for AI.
The collaboration must be repeated until it succeeds, incurring the time cost of $\AItime{i}$ per iteration for a total expected time cost of $\AItime{i}/q_i$.

Definitions~\ref{def:manual_task} and~\ref{def:augmented_task} formalize the two modes of performing a single step explicitly.

\begin{definition}[Manual Step]
\label{def:manual_task}
A step $i$ is said to be performed manually if it is executed entirely by a human worker without AI assistance.
The associated skill and time costs for a manual step are denoted by $(\manualSkill{i}, \manualTime{i})$.
\end{definition}

\begin{definition}[Augmented Step]
\label{def:augmented_task}
A step $i$ is said to be augmented if it is executed by the AI, after which its output is reviewed and approved by a human worker.
The associated skill and (expected) time costs of managing a single augmented step are denoted by $(\AIskill{i}, \frac{\AItime{i}}{q_i})$, where $q_i \in (0,1]$ is the AI's probability of successfully completing the step.
\end{definition}



\subsection{Tasks}
\label{sec:model.tasks}

Tasks are the basic unit of work of a human worker.  
Any step performed in isolation during the production process, either manually or in collaboration with AI augmentation, is a task.  
The associated skill and time costs for the resulting task are precisely the skill and time costs for the associated step performed in the chosen mode.  
Steps can also be automated by chaining them together, creating a new aggregate task.

\begin{definition}[Automated Step]
\label{def:automated_task}
A step is said to be automated if it is executed entirely by AI without direct human intervention, and its output is passed directly to a subsequent augmented or automated step. 
The direct human costs (in both skill and time dimension) associated with an automated step are zero.
\end{definition}

\begin{definition}[AI Chain]
\label{def:ai_chain}
An AI chain is a contiguous block of one or more sequential steps executed by AI, in which all steps but the final one are automated and the final step is augmented.
An AI chain spanning steps $(s_\ell,\dots,s_r)$ has steps $(s_\ell,\dots,s_{r-1})$ automated and step $s_r$ augmented.
The skill and (expected) time costs of this AI chain are given by:
\[
\left(\AIskill{r}, \frac{\AItime{r}}{\prod_{i=\ell}^{r} q_i}\right),
\]
where $q_i$ denotes the AI success probability for step $s_i$.
\end{definition}

We can think of an AI chain as a single aggregate task that is being delegated to an AI.
Successful completion requires that the AI complete all steps in $(s_\ell, \dotsc, s_r)$.
The human worker who manages the AI execution of this chain need only prompt for and evaluate the goal step, $s_r$; all other steps in the chain are assumed to be fully automated ``under the hood'' and hence beneath the awareness of the human worker.
Managing an AI attempt at the chain therefore has the same costs as augmenting step $s_r$: namely, skill cost $\AIskill{r}$ and time cost (per attempt) $\AItime{r}$.
Successful completion of the chain requires that the AI complete \emph{every} constituent step successfully.
Assuming independent failures, this occurs with probability $\prod_{i=\ell}^r q_i$, which we can view as the success probability for the aggregate chained task.
Putting this all together yields skill and expected time costs $(\AIskill{r}, \AItime{r} / \prod_{i=\ell}^{r} q_i)$ for the AI chain, as described in Definition~\ref{def:ai_chain}.

Note also that since $q_i = \alpha^{d_i}$, where recall $d_i$ is a measure of the difficulty of step $s_i$, the probability of successful completion of an AI chain spanning steps $(s_\ell, \dotsc, s_r)$ can be written as $\alpha^{(\sum_{i=\ell}^r d_i)}$.
We can therefore think of $\sum_{i=\ell}^r d_i$ as the total difficulty of the chain, which aggregates additively over its constituent steps.

To summarize, a task is either a manually-performed step, an AI-augmented step, or an AI chain. 
We define an \emph{AI deployment strategy} (or \emph{AI strategy} for short) as a sequence of tasks $\mathcal{T}$ that partitions the step sequence $\mathcal{S}$ into contiguous subsequences, with each singleton task being designated for either manual or AI-augmented execution and non-singleton tasks being AI chains.



\subsection{Jobs}
\label{sec:model.jobs}

A job is a subsequence of tasks that are assigned to a single human worker.
Recall that each task $T_b$ in task sequence $\T = \{T_1, \dotsc, T_n\}$ has associated skill and time costs $(\skillcost{b}, \timecost{b})$ that can depend on whether the task is being completed manually or with the aid of AI.
A job $J$ is a contiguous subsequence of tasks, say $J = (T_b, \dotsc, T_{b+\ell})$ for some $b$ and $\ell$.
We say that a partition $\mathcal{J} = (J_1, \dotsc, J_p)$ of all tasks into jobs is a \emph{job design}.

The firm hires one worker for each job in its job design $\mathcal{J}$.
The worker for job $J_j$ completes all tasks associated with their job.
The total time needed to complete all tasks in job $J_j$ is $\sum_{T_b \in J_j} \timecost{b}$.

A worker's wage is determined by the total skill required to complete their job.
The total skill required to complete the tasks in job $J_j$ is $\sum_{T_b \in J_j} \skillcost{b}$.
We then assume that a worker's wage is proportional to the skill level of their job.\footnote{
One motivation for this formulation is workers paying a human capital investment to acquire the skills necessary for a job. 
This investment must be offset by wages, and we express skill levels in units of their corresponding requisite wage. 
}
That is,
\begin{align}
\label{eq:wage}
\text{Wage}_j = \sum_{T_b \in J_j} \skillcost{b}.
\end{align}

The firm must pay workers their wage per unit of time regardless of which tasks they are assigned to complete at any given moment.\footnote{
This derivation implicitly assumes a common base wage rate; i.e., all wage differentiation is driven by the human capital cost of acquiring skills.
More generally, different tasks $T_b$ within job $J_j$ could have different base wage rates $w_b$ that could be influenced, for example, by the supply of and demand for labor of the corresponding type.
For simplicity in notation, we assume base wage rates are subsumed into the skill costs.
}
While we allow the firm to specialize its job design and partition its production process into distinct jobs, we acknowledge that there are inherent inefficiencies and frictions that are introduced when splitting work among multiple workers.
Absent such frictions in our model, it would always be optimal for a firm to specialize its workers as much as possible, assigning a distinct worker to each task of its production process. 
We therefore introduce \emph{hand-off costs} to a job design, as follows.
In addition to the time required to complete tasks, a worker may need to spend time handing off their work to another worker if $J_j$ is not the final job in the job design $\mathcal{J}$.
We will assume throughout that the hand-off time of a worker assigned to job $J_j$ depends only on the final step of job $J_j$ (see red curly arrows in Figure \ref{fig:hierarchical_production}).
That is, conditional on where the hand-off occurs in the production process, its cost does not otherwise depend on previous hand-off events.
Given step $s_i$, we write $\handofftime{i}$ to denote the additional hand-off time spent by a worker for whom the last step of their job is $s_i$.
For notational convenience we define the hand-off time for the final step $s_m$ to be zero: $\handofftime{m} = 0$.
Also for notational convenience, we will write $\handofftime{}(J_j)$ to denote the hand-off time of job $J_j$, which recall is equal to $\handofftime{i}$ if $s_i$ is the final step in job $J_j$.
Thus the total time needed to complete job $J_j$, including hand-off costs, is
\[
\handofftime{}(J_j) + \sum_{T_b \in J_j} \timecost{b}.
\]

Taking into account both time and skill requirements, the total wage bill paid to a worker assigned to job $J_j$, per unit of output, is
\begin{align}
\label{eq:wagebill}
\text{WageBill}_j = \Biggl(\sum_{T_b \in J_j} \skillcost{b} \Biggr) \Biggl(\handofftime{}(J_j) + \sum_{T_b \in J_j} \timecost{b} \Biggr).
\end{align}
Equation~\eqref{eq:wagebill} highlights two opposing forces that shape a job's boundaries.  
Adding more tasks to a worker's job increases the cumulative skill requirement and thus the wage rate for that worker.  
However, if tasks are kept separate, workers must incur additional hand-off costs at each job boundary.  
These two effects---higher wages from combining tasks versus higher hand-off costs from keeping them separate---jointly determine the optimal degree of task aggregation.  




\subsection{Firm's Organizational Structure}

Given the sequence of steps $\mathcal{S} = \{s_1, \dotsc, s_m\}$, the firm can design both the partition $\T$ of steps into tasks and the partition $\mathcal{J}$ of tasks into jobs.
The choice of $\T$ determines the time and skill requirements of each task.
Given $\T$, the choice of $\mathcal{J}$ then determines worker wage rates and time needed per unit of output (including hand-off costs).
Formally, we can write $\mathcal{P}(X)$ for the set of partitions of a sequence $X$ into contiguous subsequences.  Then the full optimization problem faced by the firm can be expressed as
\begin{align}
\label{eq:totalcost_with_handoff}
\min_{\T \in \mathcal{P}(\mathcal{S})} \
\min_{\mathcal{J} \in \mathcal{P}(\T)} \ 
\text{TotalCost}(\mathcal{J}; \T) 
= \sum_{J_j \in \mathcal{J}} \text{WageBill}_j = 
\sum_{J_j \in \mathcal{J}} \Biggl[\Biggl(\sum_{T_b \in J_j} \skillcost{b} \Biggr) \Biggl(\handofftime{}(J_j) + \sum_{T_b \in J_j} \timecost{b} \Biggr)\Biggr]
\end{align}
where recall that, for each $T_b \in \T$, $\timecost{b}$ and $\skillcost{b}$ are as described in Section~\ref{sec:model.tasks} and can depend on the selected mode of operation for individual steps.

We refer to \eqref{eq:totalcost_with_handoff} as the firm's \emph{long-term} optimization problem, as it anticipates the adjustment of worker wages to fit the skill requirements of each job and sets job responsibilities accordingly.
In Appendix~\ref{app:model_handoff_discussion}, we use a simple numerical example to show how hand-off costs limit worker specialization in the firm's optimal organizational structure, and provide a geometric representation of the optimization problem to clarify the underlying mechanisms.  

We also define a \emph{short-term} optimization exercise in which jobs and worker wages are fixed but the firm may still wish to use AI to maximize worker productivity.
This is equivalent to minimizing the time needed for a worker to perform a unit of work in their assigned job.
It therefore suffices to optimize for each job separately.
Thus, in the \emph{short-term} optimization problem, we can assume without loss of generality that the sequence of steps $\mathcal{S} = (s_1, \dotsc, s_m)$ is to be completed by a single worker paid at a (normalized) unit wage.
The resulting optimization problem faced by the firm can be expressed as
\begin{align}
\label{eq:totalcost_shortterm}
\min_{\T} \
\sum_{T_b \in \T} \timecost{b}
\end{align}
where recall that if $T_b = (s_\ell)$ is a manual task then $\timecost{b} = \manualTime{\ell}$, and otherwise if $T_b = (s_\ell, \dotsc, s_r)$ for some $\ell \leq r$ then $\timecost{b} = \frac{\AItime{r}}{\prod_{i=\ell}^{r} q_i}$ where $q_i$ is the AI's probability of successfully completing step $s_i$.