\section{Conclusion}

This paper develops a task-based framework for understanding how advances in AI reshape automation, the division of labor, firms' organizational structure, and production more generally.
By modeling production as a sequence of steps that can be aggregated into tasks and then into jobs, we show how firms optimally allocate work between humans and AI (whether in augmented or fully automated form) when doing so requires trading off gains from specialization against coordination frictions.
A central feature of the model is the possibility of AI chains, in which multiple steps are executed by AI and only the final output is verified by a human.
Chaining can overturn step-level comparative advantage logic in factor assignment and non-linearly amplify the effects of marginal improvements in AI quality.

We characterize short-run AI deployment decisions when job boundaries, and therefore the set of tasks assigned to each worker, are fixed, and the long-run joint optimization of job design and AI deployment strategy.
We show that improvements in AI quality can induce discrete reorganizations of work.
A key implication is that marginal increases in AI quality may generate little or no cost savings until a threshold is crossed, after which the optimal production structure changes discontinuously.
This helps explain why firms invest so heavily in AI capabilities even when short-run returns appear limited, and is consistent with the J-curve pattern of technology adoption \citep{brynjolfsson2021productivity} in which early adoption raises costs before the anticipated gains from reorganization are realized.

We also show how the production functions derived from firm-level cost minimization can be mapped into a CES production function at the aggregate level when firms differ in how they deploy a common, general-purpose AI technology.
Our framework therefore also allows studying the aggregate productivity and labor demand implications of improvements in AI quality through a micro-foundation for how individual firms respond to such advances.

We complement the theoretical analysis with empirical evidence consistent with three core mechanisms implied by the model.
Using a task-level dataset of AI exposure and AI execution outcomes, we find that AI-executed steps tend to appear in contiguous AI chains, that occupations with more fragmented AI-exposed steps in their workflow exhibit lower realized AI execution conditional on exposure levels, and that when comparable steps appear across occupations those adjacent to AI-executed neighbors are significantly more likely to be executed by AI themselves.
These patterns align with the central economic forces highlighted by the model: the importance of positional relationships among steps, the role of AI-able step dispersion in shaping execution outcomes, and the local complementarities created by AI chains.