\section{Optimization}

In this section we consider the optimization problems (both short-term and long-term) faced by a firm choosing how to integrate the AI technology into their production process.
We begin by studying the short-term problem of optimizing AI deployment strategy keeping job design and worker wages fixed.
We then move on to the joint optimization of deployment and job design taking into account long-term wage impacts. 



\subsection{Short-Term Optimization: AI Deployment Design}
\label{sec:optimization.short}

We begin with a ``short-term'' optimization problem: the job design and worker wages are assumed to be fixed, so the goal is to find the choice of AI strategy for a single job that minimizes the total time cost.  
This optimization problem analyzes short-run benefits of AI: where worker skills are fixed but AI can still be employed to speed up tasks through some combination of augmentation and automation.

Since the job design and worker wage are fixed, it suffices to optimize for the amount of time spent to complete a unit of work for each job separately.  
So, from this point onward, we assume that there is a single job $J$ with $m$ steps $\mathcal{S} = (s_1, \dotsc, s_m)$, and our goal is to find the sequence of tasks $\T$ that minimizes total completion time.  
It turns out that the time-optimal production strategy can be calculated via dynamic programming in $O(m^2)$ time.

\begin{proposition}
Given $m$ steps organized into a single job, the time-optimal AI strategy can be calculated in time $O(m^2)$ via dynamic programming.    
\end{proposition}
\begin{proof}
    We first note the following recursive formulation of the optimization problem. 
    For all $k \leq m$, let $C[k]$ denote the minimum time needed to complete a hypothetical job that only includes steps $1$ through $k$.  
    Note that, because of the way we defined $C[k]$, task $k$ cannot be automated in any minimum-time solution that determines $C[k]$; it can only be augmented or performed manually.  
    Note also that $C[m]$ is the time cost of our desired optimal solution.
    
    We now show how to calculate $C[k]$ recursively.  
    As a base case we have $C[0] = 0$, as the empty set of steps requires no time to complete.  
    For $k \geq 1$, $C[k]$ is the lesser of
    \[ C[k-1] + \manualTime{k} \]
    and
    \[ \min_{\ell < k} \Biggl\{ C[\ell] + \frac{\AItime{k}}{\prod_{i=\ell+1}^k q_i} \Biggr\}.
    \]
    In other words, we either complete step $k$ manually (in which case we separately optimize over steps $1$ through $k-1$) or we augment step $k$.  
    In the latter case, we then optimize over the length of the AI chain that ends with the newly-augmented step $k$.  
    This could be a singleton chain with no automation (corresponding to $\ell = k-1$), or a longer chain that automates one or more steps before step $k$ (corresponding to a choice of $\ell < k-1$).  
    For any such choice of $\ell$, we then separately optimize the production strategy for tasks $1$ through $\ell$.
    
    Using this formulation, given the values $(C[0], \dotsc, C[k-1])$, we can calculate $C[k]$ in time $O(k)$ by considering each potential choice of $\ell$.  
    Doing so for each $k = 1, 2, \dotsc, m$ yields the value of $C[m]$ (and the corresponding optimal AI strategy) in total time $O(m^2)$.
\end{proof}



\subsection{Warm-up to Long-Term Optimization: Job Design without AI}

We now move to a broader optimization problem in which the firm can reorganize job requirements and the assignment of tasks to workers.  
As a warm-up to the full joint optimization of jobs and AI deployment, we first show how to optimize the design of jobs for a fixed task structure.
We can interpret this as a labor optimization problem without AI deployment, where each step has only a single (i.e., manual) mode of completion and hence the task structure is fully determined.

\begin{proposition}
    Given a fixed sequence of tasks $\T = (T_1, \dotsc, T_n)$ with skill and time costs $\skillcost{} = (\skillcost{1}, \dotsc, \skillcost{n})$ and $\timecost{} = (\timecost{1}, \dotsc, \timecost{n})$, the cost-minimizing job design $\J$ can be computed in time $O(n^2)$ by dynamic programming.
\end{proposition}
\begin{proof}
    We first note the following recursive formulation of the optimization problem. 
    For all $k \leq n$, let $C[k]$ denote the minimum cost of a job design for tasks $1$ through $k$, \emph{including hand-off costs for task $k$}.  
    Note then that $C[n]$ is the cost of the optimal job design for all tasks, recalling that the hand-off cost for the final job (i.e., the job that includes task $n$) is always $0$.
    
    We now show how to calculate $C[k]$ recursively.  
    As a base case we have $C[0] = 0$.  
    For $k \geq 1$ we have
    \[ 
    C[k] = \min_{s < k} \Biggl\{ C[s] + \Biggl[\Biggl(\sum_{i = s+1}^k \skillcost{i} \Biggr) \Biggl(\handofftime{k} + \sum_{i = s+1}^k \timecost{i} \Biggr)\Biggr] \Biggr\}.
    \]
    In other words, we optimize over the choice of the final job $\{s+1, \dotsc, k\}$, accounting recursively for the optimal job design for remaining jobs.  
    Note that we make implicit use of the assumption that the hand-off cost $\handofftime{k}$ depends on the final task $T_k$ of this final job but is otherwise independent of the job design.  
    Using this formulation, we can calculate each $C[k]$ in time $O(k)$ by considering each potential choice of $s$.  
    Doing so for each $k = 1, 2, \dotsc, n$ yields the value of $C[n]$ (and the corresponding optimal job design) in total time $O(n^2)$.
\end{proof}



\subsection{Full Long-Term Optimization}

We now consider full joint optimization of job design and AI deployment strategy, accounting for both time and skill costs of workers assigned to the resulting jobs.  
In other words, the firm's goal is to choose both the set of AI chains to implement---yielding a vector of skill and time costs---along with a job design for the resulting tasks.


\subsubsection{Recursive Formulation of Optimization Problem}
\label{sec:recursive_formulation}

Here we present a recursive formulation of the firm's cost minimization problem. 
In Section \ref{sec:DP_approximation} we propose an approach to calculate an approximation of the optimal solution via dynamic programming.

Consider a production process with $m$ steps $\mathcal{S} = \{s_1, s_2, \ldots, s_m\}$.
For $0 \leq i \leq m$, let $V(i)$ denote the minimum cost required to complete steps $1$ through $i$ using one or more jobs, including any hand-off costs to a subsequent worker.  
Note then that $V(m)$ is the solution to the desired optimization problem, recalling that the hand-off time for the final job will always be $0$.  
Note also that it is implicitly assumed in the definition of $V(i)$ that it optimizes over job designs for steps $1$ through $i$ in which the final job terminates after the completion of step $i$.

It will also be helpful to consider optimal designs for steps $1$ through $i$ in which the final job doesn't necessarily terminate after the completion of step $i$, but rather continues onward to subsequent steps.  
To that end, we introduce an auxiliary function $W(i,\; \skillcost{},\; \timecost{})$.
This function denotes the minimum cost of completing steps $1$ through $i$, as well as some additional (but unspecified) set of tasks that have already been assigned as a single job to a single worker (referred to as the ``active worker'').  
It is assumed that the tasks assigned to the active worker have total time cost $\timecost{}$ and total skill cost $\skillcost{}$.  
The time cost $\timecost{}$ is assumed to already include any hand-off cost for this active worker (which recall depends only on the final step of the worker's final task). 
Crucially, the minimum is taken over all AI deployment strategies and job designs, including those that expand the number of tasks assigned to the active worker (e.g., by including step $i$ in the active worker's job).
In this sense, $W(i,\; \skillcost{},\; \timecost{})$ captures the minimum cost across all feasible job designs and AI strategies that may potentially expand the active worker's task assignment.

Note that, for all $i \leq n$, we have 
\[ V(i) = W(i,\; 0,\; \handofftime{i}). \]
This is because, in $V(i)$, all job designs must end with a job that completes at step $i$ and hands off to the following worker.  
Consequently, the hand-off cost associated with step $i$ must be incurred by the final worker.
Equivalently, this can be thought of as assigning the active worker an additional task with zero skill requirement but a time cost equal to the hand-off cost of step $i$ right after step $i$ itself.
This scenario is represented explicitly by $W(i,\; 0,\; \handofftime{i})$.

Also note that, for the base case $i=0$, we have 
\[
W(0,\; \skillcost{},\; \timecost{}) 
= 
\skillcost{}\,\timecost{}, 
\quad
\text{for all $\skillcost{}, \timecost{}$}.
\]
This is because, if $i=0$, then there are no further steps to add to the job of the active worker.  
The active worker's skill and time requirements are therefore determined entirely by the steps they have already been assigned.

We are now ready to describe a recursive formulation of the function $W(i,\; \skillcost{},\; \timecost{})$ for $i \geq 1$.  
We emphasize that in the definition of $W(i,\; \skillcost{},\; \timecost{})$, the active worker has not been assigned step $i$; we can think of step $i$ as the highest-indexed step that has not yet been assigned to a worker.

\begin{proposition}[Recursive Formulation of Job Design Problem]
\label{prop:recursive_optimality}
For each $i \geq 1$, the minimum cost function $W(i,\; \skillcost{},\; \timecost{})$ satisfies the following recursive relation:
\begin{align*}
W(i,\; \skillcost{},\; \timecost{})
= \min\Biggl\{ 
& \skillcost{}\,\timecost{} \; + \; V(i), \\
& \ W(i-1,\; \skillcost{} + \manualSkill{i},\; \timecost{} + \manualTime{i}), \\
& \ \min_{r < i} \ W\left(r,\; \skillcost{} + \AIskill{i},\; \timecost{} + \frac{\AItime{i}}{\prod_{s=r+1}^{i} q_s}\right)
\Biggr\}.
\end{align*}
The cost of the optimal joint AI strategy and job design for a given sequence of $m$ steps is then $V(m) = W(m,\; 0,\; 0)$.
\end{proposition}

The recursive formulation in Proposition~\ref{prop:recursive_optimality} evaluates the minimum cost among three distinct alternatives at each step:
\begin{itemize}
    \item \textbf{Option (1):} The term $\skillcost{}\,\timecost{} \; + \; V(i)$ corresponds to not adding any further steps to the job of the active worker.  
    All steps $1$ through $i$ will be completed by other workers. 
    The active worker's total cost is then $\skillcost{}\,\timecost{}$, and $V(i)$ is the total cost of completing steps $1$ through $i$ (including hand-off costs to the active worker).

    \item \textbf{Option (2):} The term $W(i-1,\; \skillcost{} + \manualSkill{i},\; \timecost{} + \manualTime{i})$ corresponds to designating step $i$ for manual completion, and adding the corresponding (singleton) task.
    In this case, the manual execution costs $(\manualSkill{i}, \manualTime{i})$ of step $i$ are added to the accumulated costs of tasks already assigned to the active worker, extending their job to include step $i$ as well.

    \item \textbf{Option (3):} The term $\min_{r < i} \ W\left(r,\; \skillcost{} + \AIskill{i},\; \timecost{} + \frac{\AItime{i}}{\prod_{s=r+1}^{i} q_s}\right)$ corresponds to creating an AI chain task for steps $r+1$ through $i$, with step $i$ being augmented and steps $r+1$ through $i-1$ automated, and assigning the resulting task to the job of the active worker. 
    Step $i$ is thus chained with zero or more preceding (automated) steps, and the associated AI management costs are added to the active worker's skill and time costs. 
    The index $r$ corresponds to the highest-index step that is not added to this AI chain, which can be any value between $0$ and $i-1$.
\end{itemize}
Note that in evaluating option (3) of the recursive step for $W(i,\; \skillcost{},\; \timecost{})$, step $i$ can only be augmented (rather than automated) as each step of the recursion adds a full AI chain to an active worker's job.
AI strategies in which step $i$ is automated are considered when performing task calculations $W(r, \skillcost{}, \timecost{})$ with $r > i$.



\subsubsection{Calculating an Approximately Optimal Solution}
\label{sec:DP_approximation}

Given our recursive formulation, we wish to use dynamic programming to solve for the jointly optimal job design and AI strategy by filling in the values of $W(i,\; \skillcost{},\; \timecost{})$ for all $i$, $\skillcost{}$, and $\timecost{}$.  
Since $\skillcost{}$ and $\timecost{}$ take on continuous values, we will discretize all skill costs $\skillcost{}$ and time costs $\timecost{}$ to appropriate powers of $(1+\epsilon)$, where $\epsilon > 0$ is an arbitrarily small error term.  
We obtain the following result.

\begin{proposition}
\label{prop:totalcost_optimization_dp}
    Fix any sequence of $m$ steps $\mathcal{S} = (s_1, \dotsc, s_m)$ for which all skill costs, time costs, and hand-off costs lie in $[1/B, B]$ for some $B > 0$.  Then for any $\epsilon > 0$, an approximately cost-minimizing pair of AI strategy $\T$ and job design $\J$ minimizing expression \eqref{eq:totalcost_with_handoff} to within a factor of $(1+\epsilon)$ can be computed in time $O(m^2 \epsilon^{-2} \log^2(mB) )$ by dynamic programming.
\end{proposition}

\begin{proof}
The first step of proving Proposition~\ref{prop:totalcost_optimization_dp} is to determine the range of powers of $(1+\epsilon)$ that we must consider in our discretization. 
Suppose that all manual and augmented skill and time costs, as well as all hand-off costs, lie in $[1/B, B]$ for some $B > 0$.  
%That is, these parameters require $O(\log B)$ bits to represent.  
In this case, note that any subsequence of steps could be completed at a total cost of at most $2mB^2$ by performing them all manually by different workers, incurring a  time and hand-off cost of at most $B$ each for a total time of $2B$, and a skill cost of at most $B$ for a total cost of $2B^2$ for each of the $m$ tasks. 
We therefore need not consider any solution containing a job with total cost greater than $2mB^2$.  
In particular, since any non-zero skill cost for any job is at least $1/B$, we need not consider any job design in which a job has total time cost greater than $2mB^3$.
Furthermore, each job has total skill cost lying between $1/B$ and $mB$ (as skill costs combine additively) and time cost at least $1/B$ (as each step's manual cost is at least $1/B$, and any AI chain's time cost is at least the management cost of its final step which is also at least $1/B$).

We conclude that when filling table $W(i, \skillcost{}, \timecost{})$, it suffices to consider skill costs $\skillcost{}$ lying in the range $[1/B, mB]$ and time costs $\timecost{}$ lying in the range $[1/B, 2mB^3]$.  There are $O(\epsilon^{-1} \log(mB))$ powers of $(1+\epsilon)$ in each of these ranges, so our table will have $O(m \epsilon^{-2} \log^2(mB))$ total entries. 
Each entry can be filled in time $O(m)$ by considering the recursive formulation in Proposition~\ref{prop:recursive_optimality}, for a total runtime of $O(m^2 \epsilon^{-2} \log^2(mB))$.

Note that while the table formally describes only the cost of a solution and not the solution itself, one can also read off the corresponding task and job design as well.  
Indeed, by recording which of the options described in Proposition~\ref{prop:recursive_optimality} achieves the minimum for each table entry $W(i, \skillcost{}, \timecost{})$, one can trace out the corresponding task and job designs starting with $V(m) = W(m, 0 , 0)$.  
The pair of AI strategy $\T$ and job design $\J$ can therefore be computed in time $O(m^2 \epsilon^{-2} \log(mB) )$, the same as the time required to fill the table.

It remains to bound the error introduced by our discretization.  
Consider the recursive formulation in Proposition~\ref{prop:recursive_optimality} and suppose that $\skillcost{}$ and $\timecost{}$ are rounded down to the nearest power of $(1+\epsilon)$.  
Since time and skill costs are multiplied together to calculate the total cost of a proposed job, this discretization introduces a multiplicative error of at most $(1+\epsilon)^2$ into our cost calculation for the first option when minimizing in the recursive definition of $W(i, \skillcost{}, \timecost{})$. 
For the other two options, note that we accumulate time and skill costs additively when chaining tasks together for a single worker.  
As $\skillcost{}$ and $\timecost{}$ are rounded to a power of $(1+\epsilon)$, adding additional (accurate) skill and time costs and subsequently rounding maintains a multiplicative error of at most $(1+\epsilon)$ on the total time and skill costs.  

We conclude that if we fill in our table for all $W(i,\; \skillcost{},\; \timecost{})$ where $i \leq m$ and $\skillcost{}$ and $\timecost{}$ are discretized into powers of $(1+\epsilon)$, rounding down to nearest values of $(1+\epsilon)$ on recursive calls into the table, we obtain a $1 + O(\epsilon)$ approximation to the optimal solution.  
An appropriate change of variables (scaling $\epsilon$ by a constant) yields a $(1+\epsilon)$ approximation factor in total runtime $O(m^2 \epsilon^{-2} \log^2(mB))$, as claimed in Proposition~\ref{prop:totalcost_optimization_dp}.
\end{proof}